Eye-tracking measures for Anthropomorphism in Human Robot Interaction

### 2015-03-11 main.tex
More cleaning, including a separate bibliography

\usepackage{graphicx} 
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{url}

@@

\begin{document}

@@

\numberofauthors{4} %  
\author{
\alignauthor Ashish Ranjan Jha\\
       \affaddr{Master Student}\\
       \affaddr{Computer Science, EPFL}\\
       \email{ashish.jha@epfl.ch} \\
\alignauthor Kshitij Sharma \\
       \affaddr{PhD, CHILI Lab}\\
       \affaddr{EPFL}\\
       \email{kshitij.sharma@epfl.ch}
\and
\alignauthor S\'{e}verin Lemaignan
       \affaddr{PostDoc, CHILI Lab}\\
       \affaddr{EPFL}\\
       \email{severin.lemaignan@epfl.ch}
\alignauthor Pierre Dillenbourg
        \affaddr{Professor}\\
       \affaddr{EPFL}\\
       \email{pierre.dillenbourg@epfl.ch}
}

\maketitle
\begin{abstract}

@@

It is widely accepted that anthropomorphism describes a set of human-like
features of a robot (like shape, speech capabilities, facial expression).
Lemaignan et al. \cite{mc5}  refer to these characteristics as the
anthropomorphic design of the robot .  Anthropomorphism, as described by
Lemaignan et al., refers to the social phenomenon that emerges from the
interaction between a robot and an user. According to Epley et al. \cite{mc4},
this includes for instance emotional states, motivations, intentions ascribed by
the user to the robot.

Anthropomorphism is seen as a special kind of social (human-like) engagement
with robots. We made an attempt to analyze anthropomorphism in a
\textit{human-robot} interaction by utilizing the gaze patterns of the
participants (who watched this interaction). These gaze patterns were compared
to the gaze patterns for a similar \textit{human-human} interaction setting. The
``human'' part of the human-robot and human-human interactions mentioned above
is only in the form of an audio command and not physically present in the scene.
Hence, we represent the interactions with $\mathcal{R}$ and $\mathcal{H}$ in
this report for the human-robot and human-human settings respectively.\\ \\
There were four hypotheses made in this experiment. We hypothesized
(\textbf{H1}) that the gaze patterns can distinguish between $\mathcal{H}$ and
$\mathcal{R}$ interaction scenarios. Further, this gaze pattern difference can
be denoted as the distribution of gaze on areas of interest in the scene.
Secondly, we hypothesized (\textbf{H2}) that the difference in gaze patterns
between $\mathcal{H}$ and $\mathcal{R}$ conditions
($\delta_{\mathcal{H},\mathcal{R}}$) correlate with the participants'
\textit{initial capital of anthropomorphism} (ICA), where the ICA was measured
as the sum of the ratings (responses) given by the participants to the questions
of the pre-questionnaire. This means that for participants whose ICA is low, the
gaze patterns should be significantly different for the $\mathcal{R}$ as
compared to that for the $\mathcal{H}$ videos and vice-versa.

We also hypothesized (\textbf{H3}) that the gaze patterns can distinguish
between high-cognitive and low-cognitive tasks. Finally, we hypothesized
(\textbf{H4}) that the cognitive priming will have an effect on the difference
between ICA and \textit{adaptive anthropomorphic perception} (AAP) \textit{i.e.}
$\Delta_{ICA,AAP}$ (where AAP is measured for the post-questionnaire in a
similar way as the ICA). \\ \\ We used stationary eye tracking technique for
tracking the gaze patterns and ``Nao"\cite{mc3}, a robot manufactured by
Aldebaran Robotics was used in this experiment. We prepared the scripts for the
robot using Choreographe. The interactions were recorded as videos and were then
shown to the participants. The scenarios that were covered in the videos were
aimed at eliciting the human-like or high-cognitive (HC) feelings for the robot
in one setting and robot-like or low-cognitive (LC) feelings in the other
setting. For example, we had a scene, where the robot is asked by the human to
\textit{``pick up the brown toy"} and in another scene, with the same video, the
robot is asked to \textit{``pick up its favorite toy"}. We tried to keep our
distribution of participants uniform across all variations of the scenarios to
avoid any biases to our results. The change in the feelings of participants were
recorded in the form of response to two questionnaires before and after the
experiment. The difference in the response of the two questionnaires was used to
measure the impact the videos had on the participants. \\ \\ As mentioned
earlier, the human element in the $\mathcal{R}$ interaction was in the form of
only a human voice, basically a command given by the human to the robot. This
command (\textit{e.g} ``pick up the brown toy") was used to prime the context
thereby classifying the scenario as LC or HC. Initially we had three different
scenarios where the robot/human was asked:\\ \\ (i) \ \ to pick up a toy \\ (ii)
\ to point to a sound/noise \\ (iii) to show some movements (or dance) \\ \\
Differing from first two scenarios, the third scenario had only one object in
the video i.e. the actor (human or robot). In the first two scenarios, a
participant could make gaze transitions, say, between the robot and the toys for
the first scene. In contrast, in the third scene, a participant could only look
at the robot showing its movements. The third scene, hence, was more related to
observing the various body movements and was not helpful in identifying
differences in gaze patterns based on LC and HC scenarios and therefore, we did
not consider it for our study. First, a pilot experiment was conducted with a
small number of participants and then a full-fledged experiment was carried out.

@@

In a human-robot interaction, studying anthropomorphism would essentially mean
the assessment of human's tendency to engage in a human like way with robots
(that are not deliberately made to buttress such relationship). In broader
terms, anthropomorphism can be understood as the phenomenon between a human and
a non-human, where the human tends to attribute human characteristics to the
non-human in order to establish a meaningful contact\cite{c9}. But there have
been a plethora of definitions of anthropomorphism not only across but within
disciplines(Duffy, 2002)\cite{mc1}. Even within HRI (human robot interaction)
and robotics, there has not been a single unique definition of anthropomorphism,
but a variety of them. Bartneck et al. (2008, p. 74)\cite{mc2} refer to it as
\textit{``the attribution of a human form, human characteristics, or human
behavior to nonhuman things such as robots, computers, and animals."}
Contrarily, Waytz et al. (2010)\cite{c2} apply a more psychological-cognitive
view and define anthropomorphism as \textit{``a process of inductive inference
whereby people imbue the real or imagined behavior of other agents with human
like characteristics, motivations, intentions, or underlying mental states".} \\
\\ Etymologically, anthropomorphism is a term composed of two Greek words :
\textit{anthropos} for ``man" (or ``human") and \textit{morphe} for ``from /
structure" (or ``shape"). Although anthropomorphism" literally would mean
``human form", it should \textit{not} be used to refer to the \textit{form/
design} of a non-human agent. The term \textbf{anthropomorphic design} would
rather be a better choice to refer to imitating human-like form / design of a
robot. Bartneck and Forlizzi (2004b)\cite{c3} recommend that \textit{form}
refers not just to the physical shape of a robot but to all ascertainable parts
of it. Therefore, ``form" could be seen as the overall expression of the robot,
that includes its shape, materials, and behavioral characteristics.
Anthropomorphic form can be broadly classified, but there is no fine line
dividing these categories: anthropomorphic, caricatured, functional,
zoomorphic, (Fong et al., 2003a)\cite{c4}.

Another key aspect in the discussion of anthropomorphism is the change in
people's perception of robots over their time of interaction with robots. And as
the perception changes, the tendency to anthropomorphize the robot is likely to
change. Such a gap related to the perceived agency of the robot was discussed by
Takayama (2012)\cite{c6}. She noticed that among people who own a robot, while
some people perceive their robot as an agentic object, others feel  it as only a
plain machine. In order to distinguish between these two patterns and make sense
out of them in relation to people's perception of robots in general, Takayama
differentiated between what she calls an \textit{in-the-moment} and a
\textit{reflective} perspective on agency. Hence, an \textit{in-the-moment}
perspective would refer to one's most immediate response/sense in a given
situation. On the other hand, a \textit{reflective} perspective would indicate
one's reaction/sense of a situation based on a more in-depth  consideration and
contemplation (Takayama, 2012)\cite{c6}. \\ \\ Quite often, these two
distinctions are not considered differently, leading to errors and confusions.
In other words, in an initial phase of interaction with a non-human agent,
people might respond ``mindlessly" instead of responding consciously (Nass and
Moon, 2000)\cite{c7}. Only post a due amount of time of, what is generally
called as ``familiarization" with the robot, one might respond in a more
reflective manner instead of an in-the-moment reaction. This can be demonstrated
by the fact that when participants who had interacted with a technology, were
asked about whether the interaction with the technology was in a human-like way,
most of them denied this which shows the reflective perspective . However, the
same participants had actually reacted ( in the moment of the interaction) to
the system in many ways that were quite close to how they would react to people
(Reeves and Nass, 1996)\cite{c8}.

@@

This variable was kept between subject, i.e., a participant was either shown a
LC or a HC scenario, not both. So, out of the 40 participants, 22 watched the HC
tasks and 18 watched the LC tasks.

@@

This variable was kept within subject, \textit{i.e.} a participant watched both
human as well as robot videos for either LC or HC task. To avoid any order
effect among the human and robot videos for a participant, we had an equal
distribution among participants where 20 of them watched human videos before the
robot videos and the other 20 watched the videos in reverse order (robot videos
before human)

@@

\begin{figure}
    \subfigure[$\mathcal{R}$ : Toy Scene (without AOIs)]
    {\includegraphics[width=3.3in]{stimulus-toys}\label{Toy Scene (without AOIs)}}
    \subfigure[$\mathcal{R}$ : Toy Scene (with AOIs)]
    {\includegraphics[width=3.3in]{aoi-robot}\label{Toy Scene(with AOIs)}}
    \subfigure[$\mathcal{H}$ : Sound Scene (with AOIs)]
    {\includegraphics[width=3.3in]{aoi-human}\label{Sound Scene(with AOIs)}}
    \caption{Areas of interest (AOI)}
\end{figure}

@@

The participants were asked to fill a questionnaire which had 49 questions. The
responses to the questions were scaled in the 5-point likert scale, numerically
ranging from -2 to 2. The questionnaire had ten questions from the 10 item
big-five personality questionnaire. And then there were questions taken from
godspeed questionnaire and other questionnaires. Please refer to the appendix
for a sample questionnaire used in this study. The ICA was calculated as the sum
of the ratings/points provided by the participants for questions 30 to 39 as
these were the questions most closely resembling anthropomorphism. In this
report, we refer to this questionnaire as the pre-questionnaire i.e. before the
experiment, and it typically took 5 minutes for participants to fill it.

@@

Participants on an average were around 21 years of age, with a standard
deviation of 4.5 . Among 40 participants, 21 were females and 19 were males.  We
tried and managed to avoid having participants from Computer Science or
Electronics background as they are generally perceived to have a lower
anthropomorphic attitude by default. As per our questionnaire responses, we
observed that the participants were not so familiar with robots and only a few
out of 40 had ever owned a robot.

It took approximately 15 minutes per participant for one experiment session.
Each participant was invited for only one session.

@@

After the pre questionnaire, we kept a 2 to 3 minutes session for initial
interaction, where we let the participant spend some time with Nao\cite{mc3}.
The purpose of this interaction was to familiarize the participants with the
robot and mitigate the novelty effect, so that they do not get surprised seeing
a robot for the first time in the videos.

@@

Based on the experiments conducted on 40 participants in the $\mathcal{H}$ and
$\mathcal{R}$ interactions across LC and HC conditions, we have the following
results. (The detailed statistics and code used for obtaining the results are
available here : \\
\textit{https://github.com/chili-epfl/anthropomorphism-eyetracking})

@@

While testing for all the 4 hypotheses, we observed no significant bias with
respect to age, gender , EPFL status, familiarity with robot and robot ownership
of the participants, i.e., there was no correlation found between these factors
and the gaze patterns in the videos.

@@

ANOVA between $\Delta_{ICA,AAP}$ and the category of cognitive task
\textit{i.e.} HC or LC tells us that $\Delta_{ICA,AAP}$ is greater for HC tasks
than that for the LC tasks (F[1,36] = 6.54, p < .05). The results are shown in
figure 3(c).

@@

Based on the results that we obtained, we can now verify our four hypotheses.
For the first hypothesis where we state that the gaze patterns can distinguish
between $\mathcal{H}$ and $\mathcal{R}$ interaction scenarios, we get greater
amount of fixation on the head, arms and torso for the $\mathcal{H}$ scenario as
compared to the $\mathcal{R}$ scenario. This can be explained by the fact that
human is by default perceived as a high cognitive agent compared to a robot.
Hence, the proportion of time spent on looking at the head is more in case of
human videos as compared to robot videos. But the trend is opposite for legs.
This might be explained by the fact that the participants are fascinated by the
joints on the robot's legs \textit{i.e.} the novelty effect. Overall, this
result weakly validates our hypothesis.

@@

In our experiment, we created two kinds of scenarios each for $\mathcal{H}$ and
$\mathcal{R}$ interaction and just by changing the audio commands (priming
effect), we replicated these videos to create a HC and a LC scene. We recorded
the gaze patterns of the 40 participants who were made to watch these videos and
also the participants were asked to fill two questionnaires before and after the
experiment. These data were analyzed and compared to our four hypotheses. We
hypothesized that one who anthropomorphizes more would have a similar reaction
to $\mathcal{H}$ and $\mathcal{R}$ conditions, and also that in the HC case, a
participant's fixations would be more on the head of the actor as compared to
that in the LC case. We also hypothesized that the HC scene would induce more
anthropomorphic attitude than the LC scene. We found that the results were
successful and supported our hypotheses. We also had another scenario where the
robot/human was asked to move/dance, but this scenario had only one object
(\textit{i.e.} the actor) showing movements, and hence participants would focus
more on seeing the movements leaving behind the cognition aspect, which made it
difficult to differentiate between the LC and HC cases and, therefore, we
discarded this scenario from our analysis.

\begin{thebibliography}{99}

\bibitem{mc5}S. Lemaignan, J. Fink, P. Dillenbourg, The Dynamics of Anthropomorphism in Robotics, 2014

\bibitem{mc4}N. Epley, A. Waytz, S. Akalis, and J. T. Cacioppo, ``When we need a human: Motivational determinants of anthropomorphism,'' Social Cognition,
vol. 26, no. 2, pp. 143-155, Apr. 2008.

\bibitem{mc3}NAO NEXT Gen H25 Datasheet. Aldebaran Robotics. 
December 2011.

\bibitem{c9}Fink, J., September 2014. Dynamics of Human-Robot 
Interaction in Domestic Environments (EPFL).

\bibitem{mc1}Duffy, B. R., 2002. Anthropomorphism and robotics. AISB'02: Social Intelligence and Interaction
in Animals, Robots and Agents. SSAISB, Imperial College, London, UK.
%URL http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.60.297

\bibitem{mc2}Bartneck, C., Kuli\'{c}, D., Croft, E., Zoghbi, S., Nov. 2008. Measurement instruments for the
anthropomorphism, animacy, likeability, perceived intelligence, and perceived safety of robots.
International Journal of Social Robotics 1 (1), 71-81.
%URL http://www.springerlink.com/content/d422u846113572qn/

\bibitem{c2}Waytz, A., Morewedge, C. K., Epley, N., Monteleone, G., Gao, J.-H., Cacioppo, J. T., Sep. 2010.
Making sense by making sentient: effectance motivation increases anthropomorphism. Journal
of personality and social psychology 99 (3), 410-435.

\bibitem{c3} Bartneck, C., Forlizzi, J., 2004b. Shaping human-robot interaction: understanding the social
aspects of intelligent robotic products. In: CHI '04 extended abstracts on Human factors in
computing systems. CHI EA '04. ACM, New York, NY, USA, p. 1731-1732.
%URL http://doi.acm.org/10.1145/985921.986205

\bibitem{c4}Fong, T., Nourbakhsh, I., Dautenhahn, K., Mar. 2003a. A survey of socially interactive robots.
Robotics and Autonomous Systems 42 (3-4), 143-166.
%URL http://www.sciencedirect.com/science/article/pii/S092188900200372X

%\bibitem{c5}Persson, P., Laaksolahti, J., L\"{o}nnqvist, P., 2000. Anthropomorphism: a multi-layered phenomenon.
%North Falmouth, Massachusetts, USA.
%URL http://soda.swedish-ict.se/3187/

\bibitem{c6}Takayama, L., Jan. 2012. Perspectives on agency interacting with and through personal robots. In:
Zacarias, M., Oliveira, J. V. d. (Eds.), Human-Computer Interaction: The Agency Perspective.
No. 396 in Studies in Computational Intelligence. Springer Berlin Heidelberg, pp. 195-214.
%URL http://link.springer.com/chapter/10.1007/978-3-642-25691-2_8

\bibitem{c7}Nass, C., Moon, Y., Jan. 2000. Machines and mindlessness: Social responses to computers.
Journal of Social Issues 56 (1), 81-103.
%URL http://onlinelibrary.wiley.com/doi/10.1111/0022-4537.00153/abstract

\bibitem{c8}Reeves, B., Nass, C., 1996. The Media Equation: How People Treat Computers, Television, and
New Media Like Real People and Places. Cambridge University Press.

%\bibitem{c10}NAO NEXT Gen H25 Datasheet. Aldebaran Robotics.

\end{thebibliography}

>>>>

\usepackage[utf8x]{inputenc}

\usepackage{graphicx} 
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{url}
\usepackage{xspace}

@@

\newcommand{\eg}{{\textit{e.g.\xspace}}}
\newcommand{\etal}{{\textit{et al.\xspace}}}
\newcommand{\ie}{{\textit{i.e.\xspace}}}

@@

\numberofauthors{1} %  
\author{
\alignauthor Ashish Ranjan Jha, Kshitij Sharma, Séverin Lemaignan, Pierre Dillenbourg\\
    \affaddr{CHILI Lab, École Polytechnique Fédérale de Lausanne}\\
       \email{firstname.lastname@epfl.ch}
}

\begin{document}
\maketitle
\begin{abstract}

@@

It is widely accepted that anthropomorphism describes a set of human-like
features of a robot (like shape, speech capabilities, facial expression).
Lemaignan~\etal~\cite{lemaignan2014dynamics}  refer to these characteristics as the
anthropomorphic design of the robot .  Anthropomorphism, as described by
Lemaignan~\etal, refers to the social phenomenon that emerges from the
interaction between a robot and an user. According to Epley~\etal
\cite{epley_when_2008},
this includes for instance emotional states, motivations, intentions ascribed by
the user to the robot.

Anthropomorphism is seen as a special kind of social (human-like) engagement
with robots. We made an attempt to analyze anthropomorphism in a
\textit{human-robot} interaction by utilizing the gaze patterns of the
participants (who watched this interaction). These gaze patterns were compared
to the gaze patterns for a similar \textit{human-human} interaction setting. The
``human'' part of the human-robot and human-human interactions mentioned above
is only in the form of an audio command and not physically present in the scene.
Hence, we represent the interactions with $\mathcal{R}$ and $\mathcal{H}$ in
this report for the human-robot and human-human settings respectively.

There were four hypotheses made in this experiment. We hypothesized
(\textbf{H1}) that the gaze patterns can distinguish between $\mathcal{H}$ and
$\mathcal{R}$ interaction scenarios. Further, this gaze pattern difference can
be denoted as the distribution of gaze on areas of interest in the scene.
Secondly, we hypothesized (\textbf{H2}) that the difference in gaze patterns
between $\mathcal{H}$ and $\mathcal{R}$ conditions
($\delta_{\mathcal{H},\mathcal{R}}$) correlate with the participants'
\textit{initial capital of anthropomorphism} (ICA), where the ICA was measured
as the sum of the ratings (responses) given by the participants to the questions
of the pre-questionnaire. This means that for participants whose ICA is low, the
gaze patterns should be significantly different for the $\mathcal{R}$ as
compared to that for the $\mathcal{H}$ videos and vice-versa.

We also hypothesized (\textbf{H3}) that the gaze patterns can distinguish
between high-cognitive and low-cognitive tasks. Finally, we hypothesized
(\textbf{H4}) that the cognitive priming will have an effect on the difference
between ICA and \textit{adaptive anthropomorphic perception} (AAP) \ie
$\Delta_{ICA,AAP}$ (where AAP is measured for the post-questionnaire in a
similar way as the ICA).

We used stationary eye tracking technique for tracking the gaze patterns and
``Nao", a robot manufactured by Aldebaran Robotics was used in this
experiment. We prepared the scripts for the robot using Choreographe. The
interactions were recorded as videos and were then shown to the participants.
The scenarios that were covered in the videos were aimed at eliciting the
human-like or high-cognitive (HC) feelings for the robot in one setting and
robot-like or low-cognitive (LC) feelings in the other setting. For example, we
had a scene, where the robot is asked by the human to \textit{``pick up the
brown toy"} and in another scene, with the same video, the robot is asked to
\textit{``pick up its favorite toy"}. We tried to keep our distribution of
participants uniform across all variations of the scenarios to avoid any biases
to our results. The change in the feelings of participants were recorded in the
form of response to two questionnaires before and after the experiment. The
difference in the response of the two questionnaires was used to measure the
impact the videos had on the participants.

As mentioned earlier, the human element in the $\mathcal{R}$ interaction was in
the form of only a human voice, basically a command given by the human to the
robot. This command (\eg ``pick up the brown toy") was used to prime
the context thereby classifying the scenario as LC or HC. Initially we had three
different scenarios where the robot/human was asked:

\begin{enumerate}
    \item to pick up a toy
    \item to point to a sound/noise
    \item to show some movements (or dance)
\end{enumerate}

Differing from first two scenarios, the third scenario had only one object in
the video \ie~the actor (human or robot). In the first two scenarios, a
participant could make gaze transitions, say, between the robot and the toys for
the first scene. In contrast, in the third scene, a participant could only look
at the robot showing its movements. The third scene, hence, was more related to
observing the various body movements and was not helpful in identifying
differences in gaze patterns based on LC and HC scenarios and therefore, we did
not consider it for our study. First, a pilot experiment was conducted with a
small number of participants and then a full-fledged experiment was carried out.

@@

In a human-robot interaction, studying anthropomorphism would essentially mean
the assessment of human's tendency to engage in a human like way with robots
(that are not deliberately made to buttress such relationship). In broader
terms, anthropomorphism can be understood as the phenomenon between a human and
a non-human, where the human tends to attribute human characteristics to the
non-human in order to establish a meaningful contact\cite{fink2014dynamics}. But
there have been a plethora of definitions of anthropomorphism not only across
but within disciplines\cite{duffy_anthropomorphism_2002}. Even
within HRI (human robot interaction) and robotics, there has not been a single
unique definition of anthropomorphism, but a variety of them.
Bartneck~\etal\cite{bartneck_measurement_2008} refer to it as \emph{``the
attribution of a human form, human characteristics, or human behavior to
nonhuman things such as robots, computers, and animals."} Contrarily,
Waytz~\etal\cite{Waytz2010} apply a more psychological-cognitive view and
define anthropomorphism as \textit{``a process of inductive inference whereby
    people imbue the real or imagined behavior of other agents with human like
    characteristics, motivations, intentions, or underlying mental states".}

Etymologically, anthropomorphism is a term composed of two Greek words :
\textit{anthropos} for ``man" (or ``human") and \textit{morphe} for ``from /
structure" (or ``shape"). Although anthropomorphism" literally would mean
``human form", it should \textit{not} be used to refer to the \textit{form/
design} of a non-human agent. The term \textbf{anthropomorphic design} would
rather be a better choice to refer to imitating human-like form / design of a
robot. Bartneck and Forlizzi\cite{bartneck_shaping_2004} recommend that \emph{form}
refers not just to the physical shape of a robot but to all ascertainable parts
of it. Therefore, ``form" could be seen as the overall expression of the robot,
that includes its shape, materials, and behavioral characteristics.
Anthropomorphic form can be broadly classified, but there is no fine line
dividing these categories: anthropomorphic, caricatured, functional,
zoomorphic (Fong \etal \cite{fong_survey_2003}).

Another key aspect in the discussion of anthropomorphism is the change in
people's perception of robots over their time of interaction with robots. And as
the perception changes, the tendency to anthropomorphize the robot is likely to
change. Such a gap related to the perceived agency of the robot was discussed by
Takayama \cite{takayama_perspectives_2012}. She noticed that among people who
own a robot, while some people perceive their robot as an agentic object, others
feel  it as only a plain machine. In order to distinguish between these two
patterns and make sense out of them in relation to people's perception of robots
in general, Takayama differentiated between what she calls an
\emph{in-the-moment} and a \emph{reflective} perspective on agency. Hence, an
\emph{in-the-moment} perspective would refer to one's most immediate
response/sense in a given situation. On the other hand, a \emph{reflective}
perspective would indicate one's reaction/sense of a situation based on a more
in-depth  consideration and contemplation \cite{takayama_perspectives_2012}.

Quite often, these two distinctions are not considered differently, leading to
errors and confusions.  In other words, in an initial phase of interaction with
a non-human agent, people might respond ``mindlessly" instead of responding
consciously\cite{nass_machines_2000}. Only post a due amount of
time of, what is generally called as ``familiarization" with the robot, one
might respond in a more reflective manner instead of an in-the-moment reaction.
This can be demonstrated by the fact that when participants who had interacted
with a technology, were asked about whether the interaction with the technology
was in a human-like way, most of them denied this which shows the reflective
perspective . However, the same participants had actually reacted ( in the
moment of the interaction) to the system in many ways that were quite close to
how they would react to people\cite{reeves_media_1996}.

@@

This variable was kept between subject, \ie a participant was either shown a
LC or a HC scenario, not both. So, out of the 40 participants, 22 watched the HC
tasks and 18 watched the LC tasks.

@@

This variable was kept within subject, \ie a participant watched both
human as well as robot videos for either LC or HC task. To avoid any order
effect among the human and robot videos for a participant, we had an equal
distribution among participants where 20 of them watched human videos before the
robot videos and the other 20 watched the videos in reverse order (robot videos
before human)

@@

\begin{figure}
    \subfigure[$\mathcal{R}$ : Toy Scene (without AOIs)]
    {\includegraphics[width=3.3in]{stimulus-toys}\label{Toy Scene (without AOIs)}}

    \subfigure[$\mathcal{R}$ : Toy Scene (with AOIs)]
    {\includegraphics[width=3.3in]{aoi-robot}\label{Toy Scene(with AOIs)}}

    \subfigure[$\mathcal{H}$ : Sound Scene (with AOIs)]
    {\includegraphics[width=3.3in]{aoi-human}\label{Sound Scene(with AOIs)}}

    \caption{Areas of interest (AOI)}
\end{figure}

@@

The participants were asked to fill a questionnaire which had 49 questions. The
responses to the questions were scaled in the 5-point likert scale, numerically
ranging from -2 to 2. The questionnaire had ten questions from the 10 item
big-five personality questionnaire. And then there were questions taken from
godspeed questionnaire and other questionnaires. Please refer to the appendix
for a sample questionnaire used in this study. The ICA was calculated as the sum
of the ratings/points provided by the participants for questions 30 to 39 as
these were the questions most closely resembling anthropomorphism. In this
report, we refer to this questionnaire as the pre-questionnaire \ie before the
experiment, and it typically took 5 minutes for participants to fill it.

@@

Participants on an average were around 21 years of age, with a standard
deviation of 4.5. Among 40 participants, 21 were females and 19 were males.  We
tried and managed to avoid having participants from Computer Science or
Electronics background as they are generally perceived to have a lower
anthropomorphic attitude by default. As per our questionnaire responses, we
observed that the participants were not so familiar with robots and only a few
out of 40 had ever owned a robot.  It took approximately 15 minutes per
participant for one experiment session.  Each participant was invited for only
one session.

@@

After the pre questionnaire, we kept a 2 to 3 minutes session for initial
interaction, where we let the participant spend some time with Nao.
The purpose of this interaction was to familiarize the participants with the
robot and mitigate the novelty effect, so that they do not get surprised seeing
a robot for the first time in the videos.

@@

Based on the experiments conducted on 40 participants in the $\mathcal{H}$ and
$\mathcal{R}$ interactions across LC and HC conditions, we have the following
results. (The detailed statistics and code used for obtaining the results are
available here : \url{https://github.com/chili-epfl/anthropomorphism-eyetracking})

@@

While testing for all the 4 hypotheses, we observed no significant bias with
respect to age, gender, EPFL status, familiarity with robot and robot ownership
of the participants, \ie there was no correlation found between these factors
and the gaze patterns in the videos.

@@

ANOVA between $\Delta_{ICA,AAP}$ and the category of cognitive task
\ie HC or LC tells us that $\Delta_{ICA,AAP}$ is greater for HC tasks
than that for the LC tasks (F[1,36] = 6.54, p < .05). The results are shown in
figure 3(c).

@@

Based on the results that we obtained, we can now verify our four hypotheses.
For the first hypothesis where we state that the gaze patterns can distinguish
between $\mathcal{H}$ and $\mathcal{R}$ interaction scenarios, we get greater
amount of fixation on the head, arms and torso for the $\mathcal{H}$ scenario as
compared to the $\mathcal{R}$ scenario. This can be explained by the fact that
human is by default perceived as a high cognitive agent compared to a robot.
Hence, the proportion of time spent on looking at the head is more in case of
human videos as compared to robot videos. But the trend is opposite for legs.
This might be explained by the fact that the participants are fascinated by the
joints on the robot's legs \ie the novelty effect. Overall, this
result weakly validates our hypothesis.

@@

In our experiment, we created two kinds of scenarios each for $\mathcal{H}$ and
$\mathcal{R}$ interaction and just by changing the audio commands (priming
effect), we replicated these videos to create a HC and a LC scene. We recorded
the gaze patterns of the 40 participants who were made to watch these videos and
also the participants were asked to fill two questionnaires before and after the
experiment. These data were analyzed and compared to our four hypotheses. We
hypothesized that one who anthropomorphizes more would have a similar reaction
to $\mathcal{H}$ and $\mathcal{R}$ conditions, and also that in the HC case, a
participant's fixations would be more on the head of the actor as compared to
that in the LC case. We also hypothesized that the HC scene would induce more
anthropomorphic attitude than the LC scene. We found that the results were
successful and supported our hypotheses. We also had another scenario where the
robot/human was asked to move/dance, but this scenario had only one object
(\ie the actor) showing movements, and hence participants would focus
more on seeing the movements leaving behind the cognition aspect, which made it
difficult to differentiate between the LC and HC cases and, therefore, we
discarded this scenario from our analysis.

\bibliographystyle{abbrv}
\bibliography{biblio}
